# Week 09: Alternative Fuel Stations

* fuel_type_code - The type of alternative fuel the station provides
* State filter by united states (Country)
* Status code search for planned and temporarily Unavailable
* expected_date (For planned stations)
* access_code Who is allowed to access??
* owner_type_code organization that owns the fueling infrastructure
* id - unique identifier for this specific station
* facility_type - The type of facility at which the station is located


## 1.0 Read Data
```{r readData}
library(tidyverse)

df <- tidytuesdayR::tt_load(2022, week = 9)
df <- df$stations |>
    janitor::clean_names()

df |> skimr::skim()
```

## 2.0 Data Wrangling
```{r dataCleansing}
facility_data <- df |>
    filter(country == "US") |>
    filter(access_code == "public") |>
    select(
        status_code,
        facility_type
    ) |>
    mutate(
        status_code = case_when(
            status_code == "E" ~ "Available",
            status_code == "P" ~ "Planned",
            status_code == "T" ~ "Temporarily Unavailable"
        )
    ) |>
    filter(status_code == "Temporarily Unavailable") |>
    count(facility_type, status_code, sort = T) |>
    slice_head(n = 15) |>
    mutate(facility_type = str_to_lower(facility_type)) |>
    mutate(facility_type = str_replace_all(facility_type, "_", " "))
```

## 3.0 Plot
```{r}
library(showtext)
font_add_google("Special Elite", family = "special")
showtext_auto()

p1 <- facility_data |>
    ggplot() +
    # Make custom panel grid
    geom_hline(
        aes(yintercept = y),
        data.frame(y = c(0:3) * 10),
        color = "lightgrey"
    ) +
    geom_point(
        aes(
            x = reorder(str_wrap(facility_type, 5), n),
            y = n
        ),
        size = 3,
        color = "gray12"
    ) +
    geom_col(
        aes(
            x = reorder(str_wrap(facility_type, 5), n),
            y = n,
            fill = n
        ),
        position = "dodge2",
        show.legend = TRUE,
        alpha = 0.9
    ) +
    coord_polar() +
    # Annotate custom scale inside plot
    annotate(
        x = 16.7,
        y = 6,
        label = "5",
        geom = "text",
        color = "gray12",
        family = "special"
    ) +
    annotate(
        x = 16.7,
        y = 11,
        label = "10",
        geom = "text",
        color = "gray12",
        family = "special"
    ) +
    annotate(
        x = 16.7,
        y = 16,
        label = "15",
        geom = "text",
        color = "gray12",
        family = "special"
    ) +
    annotate(
        x = 16.7,
        y = 21,
        label = "20",
        geom = "text",
        color = "gray12",
        family = "special"
    ) +
    annotate(
        x = 16.7,
        y = 26,
        label = "25",
        geom = "text",
        color = "gray12",
        family = "special"
    ) +
    scale_y_continuous(
        limits = c(-10, 30),
        expand = c(0, 0),
        breaks = c(0, 10, 20, 30)
    ) +
    scale_x_discrete(
        expand = c(0, 0)
    ) +
    # New fill and legend title for number of tracks per region
    scale_fill_gradientn(
        "Quantity (n)",
        colours = c("#6C5B7B", "#C06C84", "#F67280", "#F8B195")
    ) +
    # Make the guide for the fill discrete
    guides(
        fill = guide_colorsteps(
            barwidth = 15,
            barheight = 1.5,
            title.position = "top",
            title.hjust = 0.5
        )
    ) +
    theme(
        # Remove axis ticks and text
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_blank(),
        # Use gray text for the region names
        axis.text.x = element_text(
            color = "gray12",
            size = 12,
            family = "special"
        ),
        # Move the legend to the bottom
        legend.position = "bottom",
    )


p1 +
    labs(
        title = paste(
            "\nQuantity of Public Temporarily\n",
            "Unavailable Facilities for Alternative\n",
            "Fuel Stations in the United States"
        ),
        subtitle = paste(
            "\nWhen choosing a public alternative fuel station,\n",
            "do not consider a 'fuel reseller'."
        ),
        caption = "@valdezdata | #TidyTuesday | Source: US DOT"
    ) +
    theme(
        text = element_text(
            color = "gray12", family = "special"
        ),
        plot.title = element_text(face = "bold", size = 25, hjust = 0.05),
        plot.subtitle = element_text(size = 14, hjust = 0.05),
        plot.caption = element_text(size = 10, hjust = 0.5),
        panel.background = element_rect(fill = "white", color = "white"),
        panel.grid = element_blank(),
        panel.grid.major.x = element_blank()
    )
```

## 4.0 Save
```{r}
ggsave("2022/W09_fuelStations/plot.svg", width = 9, height = 12.6)
```
