# Week 10: EU Student Mobility

Totally inspired by: <https://twitter.com/BjnNowak/status/1501138757810114561/photo/1>

-   participant_nationality - Code (DE, FR, BE, .....)
-   participant_gender - Male/Female/Undefined
-   participant_profile - Staff or learner
-   special_needs - Yes/no
-   fewer_opportunities - Yes/no
-   sending_country_code - Code (DE, FR, BE, .....)
-   sending_city - City of sending organisation
-   receiving_country_code - Code (DE, FR, BE, .....)
-   receiving_city - City of receiving organisation
-   participants - Total number of participants

## 1.0 Read Data

```{r readData}
library(tidyverse)

df <- tidytuesdayR::tt_load(2022, week = 10)
df <- df$erasmus |>
    janitor::clean_names()

# From https://github.com/BjnNowak/TidyTuesday/blob/main/SC_Erasmus.R
iso <- read_delim(
    "https://raw.githubusercontent.com/BjnNowak/TidyTuesday/main/data/iso.csv",
    delim = ";")

skimr::skim(df)
```

## 2.0 Data Wrangling

```{r}
# Send data
sending_data <- df |>
    mutate(sending_female = case_when(
        participant_gender == "Female" ~ participants,
        TRUE ~ 0
    )) |>
    mutate(sending_male = case_when(
        participant_gender == "Male" ~ participants,
        TRUE ~ 0
    )) |>
    group_by(sending_country_code) |>
    summarise(
        female_total = sum(na.omit(sending_female)),
        male_total =  sum(na.omit(sending_male)),
        sending = sum(na.omit(participants))
    ) |>
    ungroup() |>
    left_join(
        iso,
        by = c("sending_country_code" = "code")
    ) |>
    arrange(-sending) |>
    select(-sending_country_code) |>
    relocate(country_name) |>
    pivot_longer(
        cols = 2:3,
        names_to = "female_or_male",
        values_to = "count_sending"
    ) |>
    slice_head(n = 30)

# Receiving data
receiving_data <- df |>
    mutate(receiving_female = case_when(
        participant_gender == "Female" ~ participants,
        TRUE ~ 0
    )) |>
    mutate(receiving_male = case_when(
        participant_gender == "Male" ~ participants,
        TRUE ~ 0
    )) |>
    group_by(receiving_country_code) |>
    summarise(
        female_total = sum(na.omit(receiving_female)),
        male_total =  sum(na.omit(receiving_male)),
        receiving = sum(na.omit(participants))
    ) |>
    ungroup() |>
    left_join(
        iso,
        by = c("receiving_country_code" = "code")
    ) |>
    arrange(-receiving) |>
    select(-receiving_country_code) |>
    relocate(country_name) |>
    pivot_longer(
        cols = 2:3,
        names_to = "female_or_male",
        values_to = "count_receiving"
    ) |>
    slice_head(n = 30)

# Join data
exchange_tbl <- sending_data |>
    inner_join(receiving_data) |>
    select(
        country_name,
        female_or_male,
        everything()
    )
```

## 3.0 Plot

```{r}
library(showtext)
font_add_google("Hubballi")
showtext_auto()

exchange_tbl |>
    ggplot(
        aes(
            y = fct_reorder(
                country_name,
                receiving
            )
        )
    ) +
    geom_segment(
        aes(
            y = fct_reorder(
                country_name,
                receiving
            ),
            yend = fct_reorder(
                country_name,
                receiving
            ),
            x = 0,
            xend = receiving
        ),
        size = 9,
        col = "#0eac00",
        alpha = 0.15,
        inherit.aes = FALSE
    ) +
    geom_segment(
        aes(
            y = fct_reorder(
                country_name,
                receiving
            ),
            yend = fct_reorder(
                country_name,
                receiving
            ),
            x = 0,
            xend = -sending
        ),
        size = 9,
        col = "#dbd800",
        alpha = 0.15,
        inherit.aes = FALSE
    ) +
    geom_point(
        aes(
            count_sending,
            fct_reorder(country_name, count_sending),
            color = female_or_male
        ),
        size = 3,
        show.legend = FALSE,
        alpha = 0.75
    ) +
    geom_point(
        aes(
            -count_receiving,
            fct_reorder(country_name, -count_receiving),
            color = female_or_male
        ),
        size = 3,
        show.legend = TRUE,
        alpha = 0.75
    ) +
    scale_color_manual("Gender", values = c("#d70dff", "#0c4bf7")) +
    scale_x_continuous(
        position = "top",
        breaks = c(
            -30000, -20000, -10000, 10000, 20000, 30000
        ),
        labels = c(
            "30,000", "20,000", "10,000", "10,000", "20,000", "30,000"
        )
    ) +
    guides(
        size = guide_legend(
            title.position = "top", title.hjust = 0.5
        ),
        fill = guide_legend(
            title.position = "top", title.hjust = 0.5
        )
    ) +
    geom_text(
        aes(
            y = fct_reorder(
                country_name,
                receiving
            ),
            label = country_name
        ),
        x = 0,
        color = "#6e6e6e",
        alpha = 0.5
    ) +
    geom_text(
        tibble(
            y = "Czechia",
            x = -25000,
            label = "Outgoing\nStudents"
        ),
        mapping = aes(
            x = x,
            label = label
        ),
        y = "Czechia",
        inherit.aes = FALSE,
        size = 5,
        vjust = 0.5,
        family = "Huballi"
    ) +
    geom_text(
        tibble(
            y = "Czechia",
            x = 25000,
            label = "Incoming\nStudents"
        ),
        mapping = aes(
            x = x,
            label = label
        ),
        y = "Czechia",
        inherit.aes = FALSE,
        size = 5,
        vjust = 0.5,
        family = "Huballi"
    ) +
    labs(
        x = "Number of Students",
        y = "",
        title = "Student Exchanges in Europe from Erasmus Program",
        subtitle = paste(
            " Bars shows the total number of participants,",
            "dots represents the quantity of departures by gender.\n",
            "Totally inspired by @BjnNowak"
        ),
        caption = "@valdezdata | #TidyTuesday | Source: Data.Europa.eu"
    ) +
    theme_void() +
    theme(
        legend.position = "bottom",
        legend.text = element_text(
            size = 15
        ),
        legend.title = element_text(
            size = 15
        ),
        text = element_text(
            family = "Hubballi"
        ),
        plot.background = element_rect(fill = "#F5F5F5"),
        axis.text.x = element_text(size = 9),
        axis.title.x = element_text(
            size = 12,
            face = "bold",
            margin = margin(0.2, 0.2, 0.2, 0.2, unit = "cm"),
            hjust = 0.5
        ),
        axis.title = element_text(
            hjust = 0,
            size = 9,
            color = "#2A1A13"
        ),
        plot.title = element_text(
            size = 20,
            face = "bold",
            color = "#2A1A13",
            hjust = 0.05
        ),
        plot.subtitle = element_text(
            size = 15,
            face = "italic",
            color = "#2A1A13",
            hjust = 0.05
        ),
        plot.caption = element_text(
            element_text(
                size = 7
            )
        )
    )
```

## 4.0 Save

```{r}
ggsave("2022/W10_studentMobility/plot.svg", width = 9, height = 12.6)
```
